Neighbor-Based Decentralized Training Strategies for Multi-Agent Reinforcement Learning

### 2024-10-03 paper-2024-sac-marl-neighbouring-strategies.tex
fix typo sec 2

\subsection{State of the Art}
Multi-agent reinforcement learning is a longstanding research area with a rich literature, starting 
from seminal works like~\cite{tan1993multi} and~\cite{busoniu2008comprehensive} to more recent contributions like~\cite{gronauer2022multi} and~\cite{canese2021multi}.
%
In the following, we briefly discuss some of the most relevant approaches in the field.
\subsubsection{Independent Learners}
In independent learner, each agent learns its policy independently, disregarding the actions and policies of other agents. 
This straightforward approach, among the earliest explored in MARL, often relies on variants of Q-learning. 
However, independent learners struggle with coordination due to the non-stationarity introduced by the simultaneous learning of other agents.

>>>>

\subsection{State of the Art}
Multi-agent reinforcement learning is a longstanding research area with a rich literature, starting 
from seminal works like~\cite{tan1993multi} and~\cite{busoniu2008comprehensive} to more recent contributions like~\cite{gronauer2022multi} and~\cite{canese2021multi}.
%
In the following, we briefly discuss some of the most relevant approaches in the field.
\subsubsection{Independent Learners}
In independent learners, each agent learns its policy independently, disregarding the actions and policies of other agents. 
This straightforward approach, among the earliest explored in MARL, often relies on variants of Q-learning. 
However, independent learners struggle with coordination due to the non-stationarity introduced by the simultaneous learning of other agents.
